\section{WiFi-TTA-Bench: Benchmark Design}

\begin{table}[h]
\centering
\caption{Datasets and methods. The \textbf{Shape} column reports $(\text{features},\text{time/packets})$ per sample for the prepared CSI tensors used by the benchmark; the SignFi-10 row reports $(\text{flattened features},\text{prepared dim})$. Full dataset protocol, per-method hyperparameters, and absolute baselines are in Appendix~\ref{app:hyperparams}/\ref{app:datasheet}.}
\label{tab:datasets}
\small
\resizebox{\textwidth}{!}{%
\begin{tabular}{lcccc}
\toprule
\textbf{Dataset} & \textbf{Samples} & \textbf{Classes} & \textbf{Envs / Shape} & \textbf{Shift Type} \\
\midrule
Widar\_BVP~\cite{zheng2019widar} & 8,964 & 6 gestures & 3 rooms / $(22,400)$ & Cross-room \\
NTU-Fi HAR & 1,200 & 6 activities & 3 sessions / $(114,500)$ & Cross-session (temporal) \\
SignFi-10~\cite{ma2018signfi} & 200 & 10 gestures & 3 splits / $(200,90)$ & Cross-split (temporal) \\
Synthetic & config. & 3 & 2 domains / $(8,2)$ & Controlled physics \\
\bottomrule
\end{tabular}%
}
\end{table}

\textbf{Protocol.} Leave-one-environment-out for each real dataset; 3 folds $\times$ 5 seeds $=$ 15 paired observations per method. Synthetic data uses the OFDM channel model $H(f_k)=\sum_l h_l \exp(-j2\pi f_k \tau_l)$ with class-specific multipath parameters and tunable shift severity (mild/moderate/strong). NTU-Fi sessions and SignFi splits are temporal splits within a single laboratory, not verified physical-room changes (see Limitations).

\textbf{Methods (12 total: 11 TTA + \texttt{no\_adapt}).} Generic: \texttt{entropy\_tta}, \texttt{cons.~entropy}, \texttt{tent-proj}~\cite{wang2021tent}, \texttt{im} (SHOT variant)~\cite{liang2020shot}, \texttt{t3a}~\cite{iwasawa2021t3a}, \texttt{sar}~\cite{niu2023sar}, \texttt{cotta}~\cite{wang2022cotta}, \texttt{lame}~\cite{boudiaf2022lame}. Physics (ours): \texttt{physics\_tta}, \texttt{safe\_physics}, \texttt{selective\_physics}. A faithful BN-affine \texttt{tent} is added on MLP+BN for Section~\ref{sec:arch}.

\textbf{Backbone.} MLP encoder (3 layers $\times$ 64 hidden, latent dim 32) with residual-prior input $[\mathbf{x},\mathbf{p}(\mathbf{x}),\mathbf{x}-\mathbf{p}(\mathbf{x})]$; classifier head frozen during adaptation. Architecture ablation with CNN1D+BN and MLP+BN in Section~\ref{sec:arch}.

\textbf{Implementation fidelity.} The primary MLP has no BatchNorm, so TENT is implemented as projection-layer-only updates (\texttt{tent-proj})---TENT's minimal-update principle without its BN-specific mechanism. SHOT is realised as entropy minimisation $+$ class-diversity regularisation (information maximisation, \texttt{im}) without pseudo-label self-training. SAR, CoTTA, and LAME are adapted to the shared backbone. Only the MLP+BN control in Section~\ref{sec:arch} is a faithful BN-affine TENT. Selective-physics thresholds ($\tau_c{=}0.2$, $\tau_a{=}2.0$) were fixed pre-evaluation.

\textbf{Evaluation.} Five metrics per method: mean target gain, 95\% bootstrap CI (10K resamples), Cohen's $d$ vs.\ \texttt{no\_adapt}, negative adaptation rate $P(\text{gain}<0)$, source drop. With 11 TTA methods vs.\ \texttt{no\_adapt}, applying Bonferroni correction ($\alpha_{\text{corr}}\approx0.0045$) does not change the qualitative conclusion, since no method's uncorrected 95\% CI on a real dataset is positive on the primary backbone. Gain is reported as a fraction in detailed tables ($0.003{=}0.3$~pp) and in pp in prose. Source-only accuracy: Widar\_BVP 37.3\%, NTU-Fi 69.7\%, SignFi-10 $\approx$95\% (see Appendix~\ref{app:datasheet}); the Widar cross-room gap is 52.1~pp.
