\section{Limitations}

\begin{enumerate}
    \item \textbf{Method fidelity.} On the primary MLP backbone, TENT is implemented as projection-layer updates (\texttt{tent-proj}) rather than the original BN-statistic updates; SHOT is implemented as information maximisation without pseudo-label self-training; SAR, CoTTA, and LAME are adapted to the shared backbone. A faithful BN-affine TENT on MLP+BN is provided as a control.
    \item \textbf{Dataset and task scope.} Three real datasets (Widar\_BVP, NTU-Fi, SignFi-10) cover gesture and activity recognition but not localisation, vital signs, or through-wall imaging. SignFi-10 is small (200 samples, 10 classes). NTU-Fi sessions and SignFi splits are temporal within a single laboratory, not verified physical rooms.
    \item \textbf{Source overfitting and single architecture.} The Widar\_BVP source model shows a 42~pp train--val gap (89.4\% vs.\ 47.4\%), which may impair confidence-based TTA. The primary backbone is MLP (no BN); CNN1D+BN underfits real data (45.8\% source accuracy vs.\ MLP 79.9\%), so the CNN1D real-data probe is limited to one Widar room with 3 seeds.
    \item \textbf{Sample size.} The main evaluation and MLP-vs-MLP+BN control use $n{=}15$ paired observations (3 folds $\times$ 5 seeds), adequate for large effects ($d{\geq}0.8$) but underpowered for small ones. No channel estimation (the analysis bottleneck) is evaluated.
    \item \textbf{Claim scope, privacy, and release.} Evidence supports conclusions for WiFi CSI gesture/activity TTA under the evaluated splits; we do not claim universal TTA failure on physics-structured shifts (SignFi-10 + MLP+BN is a positive counterexample). WiFi CSI sensing can enable covert monitoring; we redistribute scripts and split manifests under an acceptable-use notice requiring consent, and report negative-adaptation/source-drop metrics to discourage deployment of silently-degrading adaptation. Raw datasets remain under their original academic licences.
\end{enumerate}

An extended limitations discussion, reviewer-FAQ (Q1--Q5), and full ethics statement are in Appendix~\ref{app:reviewer_faq}.
